### 2017-03-21 grlp.tex
LP edits

\section{Generalized Reduced Linear Programming}\label{sec:grlp}
The Generalized Reduced Linear Program is given as:

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Generalized Reduced Linear Programming}\label{sec:grlp}
\todoc{How about the cleaner ``Linear projected approximate linear programming''}
In this section we introduce the computational model used and the optimization problem
that is the main object of our study.
As discussed in the introduction, we are interested in methods that compute a good approximation to the optimal value function.
As noted earlier, at the expense of a modest additional cost, knowing an $O(\epsilon)$ approximation to $J^*$ at a few states suffices to compute actions of an $O(\epsilon)$-optimal policy. We will take a more general view, and we will consider calculating good approximations to $J^*$ with respect to a weighted $1$-norm, where the weights $c$ form a probability distribution over $\S$. Recall that the weighted $1$-norm $\norm{J}_{1,c}$ of a vector $J\in \R^S$ is defined as $\norm{J}_{1,c}  = \sum_s c(s) |J(s)|$. Note that here and in what follows we identify elements of $\R^\S$ (functions, mapping $\S = \{1,\dots,S\}$ to the reals) with elements of $\R^S$ in the obvious way. This allows us to write e.g. $c^\top J$, which denotes $\sum_s c(s) J(s)$.

To introduce the optimization problem we study first recall that 
the optimal value function $J^*$ is the solution of the fixed point equation $TJ^* = J^*$. 
It follows from the definition of $T$ that $J^* = \max_u T_u J^* \ge T_u J^*$ for any $u$, 
where $\ge$ is the componentwise partial ordering of vectors. 
With some abuse of notation, we also introduce $T_a$ to denote $T_u$ where $u(s) = a$ for any $s\in \S$. 
It follows that $J^* \ge T_a J^*$ for any $a\in \A$ and also that $T = \max_a T_a$, where again the maximization is componentwise.
We call a vector $J$ that satisfies $J \ge T_a J$ for any $a\in A$ \emph{superharmonic}. Note that this is a set of linear inequalities. 
By our note on $T$ and $(T_a)_a$, these inequalities can also be written compactly as $J \ge T J$.
\if0
Since $T$ is monotone (i.e., for any $J_1\le J_2$ it holds that $TJ_1 \le T J_2$) and can be seen to be an $\alpha$-contraction with respect to the maximum norm, if $J$ is superharmonic then $J \ge T J \ge T^2 J \ge \dots \ge J^*$, where the last inequality follows since $T$ is an $\alpha$-contraction and hence $T^n J \to J^*$ in the maximum norm, and hence also componentwise.
Thus, $J^*$ is the ``smallest'' superharmonic function. It follows than that 
for any $c\in \R_+^S \doteq [0,\infty)^S$ and any superharmonic $J$, $c^\top J^*\le c^\top J$ and since $J^*$ is also superharmonic, $\min \{ c^\top J\,:\, J \ge T J \} = c^\top J^*$ and if $c$ is positive-valued then the minimizer of $c^\top J$ amongst all superharminoc functions is $J^*$.
\fi
It is not hard to show then that $J^*$ is the smallest superharminoc function (i.e., for any $J$ superharmonic, $J\ge J^*$). It also follows that for any  $c\in \R_{++}^S \doteq (0,\infty)^S$, the unique solution to the linear program $\min\{ c^\top J \,:\, J \ge T J \} =\min \{ c^\top J\,:\, J \ge T_a J, a\in \A \} $ is $J^*$.

Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
\todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
The \emph{Approximate Linear Program} (ALP) of \citet{SchSei85} 
is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program. Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
\emph{For the purpose of computations, it is assumed that the values $c^\top \phi_i$, $i=1,\dots, k$ and the values $(P_a \phi_i)(s)$ and $g_a(s)$ can be accessed in constant time.} 
This assumption can be relaxed to assuming that one can access $g_a(s)$ and $\phi_i(s)$ for any $(s,a)$ in constant time, as well as to that one can efficiently sample from $c$, from $P_a(s,\cdot)$ for any $(s,a)$ pair, 
but the details of this are the beyond the scope of the present work. As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm.

While evaluating the objective and checking a single constraint for constraint violations can be done in constant time, 
since the number of constraints in the ALP is equal to the number of state-action pairs, the ALP is still intractable in general.
To reduce the number of constraints, we propose to relax the constraints by considering a linear projection of them with 
positive linear coefficients. Since the resulting program may become unbounded, it is necessary to introduce an additional constraint $r\in \N$, where $\N$ will be chosen to be large enough so as not to exclude ``good solutions'', while constraining enough so as to prevent unbounded solutions. \todoc{I still don't get whether we need or not $\N$. Under the conic constraints, do we need it or not? I mean when $r$ hits the boundary of $\N$ I have the feeling that we get a very bad solution and it would not then matter much whether $\N$ is even there or not.}
This leads to what we call the Generalized Reduced Linear Program: \todoc{Again, Linearly Projected ALP, or ALP with Linear Constraint Projection, or with Linear Constrain Relaxation?} \todoc{I stopped here, need to sleep. The idea in this section is to just explain how the computation is done. In the next section I would just give the main result. In the next section I would give the proof. Rather than the present lemma, lemma, lemma.. organization it is probably better to organize the proof in a top-down. Starting to do the proof, required results can be stated as claims/lemmas. But maybe some of the lemmas can be saved (I have a specific plan, just saying, if you want to do something with this).}

### 2017-03-21 intro.tex
LP edits

The main objective of \emph{planning} is to compute actions of an optimal policy while interacting with an MDP model. 
In finite state-action MDPs,
assuming access to individual transition probabilities and rewards along transitions, 
various algorithms are available to perform this computation in time and space that scales polynomially with the number of states and actions.
However, in most practical applications, the MDP is compactly represented
and if it is not infinite, the number of states scale \emph{exponentially} with the \emph{size of the representation} of the MDP.
%an effect that is known as \emph{Bellman's curse of dimensionality}.
If planners are allowed to perform some fixed amount of calculations for each state encountered,
it is possible to use sampling to make the per-state calculation-cost 
independent of the size of the state space \cite{rust96:randomization,szepesvari2001,kearns2002sparse}.
Nevertheless, the resulting methods are still quite limited. 
In fact, various hardness results show that computing actions of (near-) optimal policies is intractable in various senses
and in various compactly represented MDPs \cite{BlonTsi:00Complexity}.
Given these negative results, 
it is customary to adopt the \emph{modest goal of efficiently computing actions of a policy that 
is nearly as good as the best policy in a given restricted policy class}.
Here, within some restrictions (see below), the policy class can be chosen by the user.
The more flexibility the user is given in this choice, the stronger a planning method is.

@@

Most of the literature is thus devoted to designing methods to select a tractable subset of the constraints while keeping the approximation guarantees, as well as keeping computations tractable. 
For example, \citet{schuurmans} and \citet{gkp} propose constraint generation in a setting 
where the MDP has additional structure (i.e., factorized transition structure) 
that is then exploited in the constraint generation method.
A more general approach due to \citet{CS} 
is to choose a random subset of the constraints 
by choosing states to be included at random from a distribution that reflects the ``importance'' of states.
While constraint generation is powerful when applicable,
it is not known how solution quality degrades with the budget on the constraints generated.
For constraint sampling,  \citet{CS} prove a bound on the suboptimality, but this bound applies only 
in the unrealistic scenario when the constraints are sampled from an \emph{idealized} distribution,
which is related to the stationary distribution of an optimal policy. 
While it is possible to extend this result
to any sampling distribution, the bound then scales with the mismatch between the sampling and the idealized
distributions, which, in general, will be uncontrolled. 
Another weakness of the bound is related to that when constraints are dropped, the linear program may become
unbounded. To prevent this, \citet{CS}  propose adding an extra constraint on the optimization variables.
The bound they obtain, however, scales with the \emph{worst approximation error} over this constraint set.
While in a specific example it is shown that this error can be controlled, no general results are derived in this direction.
Later works, such as that of
\citet{SALP,BhatFaMo12:SALPNP},  repeat the analysis of \citet{CS}
in combinations with other ideas. However, no existing work that we know of addresses the above weaknesses of the result of \citet{CS}.

>>>>

The main objective of \emph{planning} is to compute actions of an optimal policy while interacting with an MDP model. 
In finite state-action MDPs,
assuming access to individual transition probabilities and rewards along transitions, 
various algorithms are available to perform this computation in time and space that scales polynomially with the number of states and actions.
However, in most practical applications, the MDP is compactly represented
and if it is not infinite, the number of states scale \emph{exponentially} with the \emph{size of the representation} of the MDP.
%an effect that is known as \emph{Bellman's curse of dimensionality}.
If planners are allowed to perform some fixed amount of calculations for each state encountered,
it is possible to use sampling to make the per-state calculation-cost 
independent of the size of the state space \cite{rust96:randomization,szepesvari2001,kearns2002sparse}.
Nevertheless, the resulting methods are still quite limited. 
In fact, various hardness results show that computing actions of (near-) optimal policies is intractable in various senses
and in various compactly represented MDPs \cite{BlonTsi:00Complexity}.
Given these negative results, 
it is customary to adopt the \emph{modest goal of efficiently computing actions of a policy that 
is nearly as good as the best policy \todoc{This is too ambitious still. Need to tweak.}
in a given restricted policy class}.
Here, within some restrictions (see below), the policy class can be chosen by the user.
The more flexibility the user is given in this choice, the stronger a planning method is.

@@

Most of the literature is thus devoted to designing methods to select a tractable subset of the constraints while keeping the approximation guarantees, as well as keeping computations tractable. 
Since a linear objective is optimized by a point on the boundary of the feasible region, 
knowing the optimizer would be sufficient to eliminate all but 
as many constraints as the number of optimization variables.
The question is how to find a superset of these, or an approximating set, without incurring much computational overhead.
\citet{schuurmans} and \citet{gkp} propose constraint generation in a setting 
where the MDP has additional structure (i.e., factorized transition structure).
This additional structure is then exploited in designing constraint generation methods which are able to efficiently generate
violated constraints. A more general approach due to \citet{CS} 
is to choose a random subset of the constraints 
by choosing states to be included at random from a distribution that reflects the ``importance'' of states.
While constraint generation can be powerful,
it is not known how solution quality degrades with the budget on the constraints generated
(\citeauthor{gkp} note that the number of constraints generated can be at most exponential in a fundamental quantity,
the induced width of a so-called cost-network, which may be large and is in general hard to control).
For constraint sampling,  \citet{CS} prove a bound on the suboptimality, but this bound applies only 
in the unrealistic scenario when the constraints are sampled from an \emph{idealized} distribution,
which is related to the stationary distribution of an optimal policy. 
While it is possible to extend this result
to any sampling distribution, the bound then scales with the mismatch between the sampling and the idealized
distributions, which, in general, will be uncontrolled. 
Another weakness of the bound is related to that when constraints are dropped, the linear program may become
unbounded. To prevent this, \citet{CS}  propose adding an extra constraint on the optimization variables.
The bound they obtain, however, scales with the \emph{worst approximation error} over this constraint set.
While in a specific example it is shown that this error can be controlled, no general results are derived in this direction.
Later works, such as that of
\citet{SALP,BhatFaMo12:SALPNP},  repeat the analysis of \citet{CS}
in combinations with other ideas. However, no existing work that we know of addresses the above weaknesses of the result of \citet{CS}.

### 2017-03-21 mdp.tex
LP edits

%!TEX root =  autocontgrlp.tex
\section{Background: Markov Decision Processes (MDPs)}
The framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems in stochastic environments. In this section, we present a brief overview of the MDP framework, introducing the notions of policy, value function and optimality (please refer to \cite{BertB} for a detailed presentation on MDP).

\textbf{Model:} We consider an MDP with a finite state space given by $S=\{1,2,\ldots,n\}$ and a finite action space given by $A=\{1,2,\ldots,d\}$ (where the sentiment is that $n$ is large). For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$. We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.

\textbf{Policy:} A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state. Under an SDP, an MDP is a Markov chain whose probability transition matrix is denoted by $P_u$.

\textbf{Value Function:} Given an SDP $u$, the expected total discounted reward corresponding to starting at a state $s\in S$ at $t=0$, while choosing actions as dictated by $u$ for the states encountered in the future (i.e., $t>0$), is
\begin{align}
J_u(s)\stackrel{\Delta}{=}\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
\end{align}
where $\alpha \in (0,1)$ is the so-called discount factor and $s_{t+1} \sim p_{a_t}(s_t,\cdot)$, $t\ge 0$.
We call $J_u(s)$ the value of state $s$ under SDP $u$, while $J_u$ (as a map from $S$ to the reals)
is called the value function underlying policy $u$. The value functions $J_u$ is an elements of $\R^S$. In what follows it will be useful for us to treat it as an $n$-dimensional vector, i.e., an element of $\R^n$, effectively identifying $\R^S$ with $\R^n$ in the natural way. Similarly we identify $\R^{nd}$ with $\R^{S\times A}$, where $d=|A|$.

\textbf{Optimality and the Bellman Equation:} The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state. That is, $J_{u^*}(s) = J^*(s) \eqdef \us{\max}{u\in U} J_u(s)$
where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.
\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}
Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE) which states that for all $ s \in S$,
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),~\text{and}\\
\label{bellpol}u^*(s)&\in \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),\,.
\end{align}
\end{subequations}
where ties in \eqref{bellpol} are resolved arbitrarily.

For the subsequent sections, the following definitions will be useful later:
\begin{definition}\label{notations}
\begin{comment}
Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$,
define
\end{comment}
\begin{enumerate}[(i)]
\item\label{bellopval} The Bellman operator $T\colon \R^n \ra \R^n$ is given by $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
$
\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values is given by $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
\item\label{emat} The $nd\times n$ matrix $E$ is given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
\item\label{greedy} A policy $u_J$ is said to be greedy with respect to (w.r.t.) $J\in \R^n$ if for any $s\in S$,
%some function $\tj:S \to \R$
\begin{align*} u_J(s)\in\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S} p_a(s,s')J(s')\big).\end{align*}
\item\label{norms} The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ with respect to a probability distribution $c$ is given by $
\norm{J}_{1,c}=\sum_{s \in S} c(s)|J(s)|$.
\item The (un)weighted $L_\infty$-norms $\norm{\cdot}_{1,\infty}$
and $\norm{\cdot}_{\infty,\rho}$, $\norm{J}_{\infty}=\max_{s\in S}|J(s)|$ and $\norm{J}_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
\item For $J_1, J_2\in \R^n$ we write $J_1\leq J_2$ when $J_1(s)\leq J_2(s),~\forall s\in S$.
\item We define $\one\in \R^n$ to be the vector whose coordinates are all equal to $1$.
\end{enumerate}
\end{definition}
We would like to point out that from \Cref{notations}, it follows that for any $J\in \R^n$ the condition $J\geq TJ$ can be rephrased as $EJ\geq HJ$.
\begin{comment}
\subsection{Dynamic Programming: Objective and Methods}
Once a given sequential decision making is cast in the MDP framework, it remains for us to still compute the optimal policy $u^*$. The idea behind Dynamic Programming (DP) methods is to use the BE \eqref{bellval} to first compute $J^*$, and then a near-optimal action $u^*$ can be obtained via \eqref{bellpol}
for each state relatively cheaply even for large state-spaces (e.g., having the ability to sample from the next-state distribution at
a given state-action pair). Thus computing $J^*$ is at the heart DP methods \cite{BertB} such as value-, or policy-iteration and linear programming (LP) \eqref{mdplp} which can be used in practice when the MDP has a tractable number of states. However, when the MDP has a large number of states, using DP methods to obtain $J^*$ is tedious, since they involve computations in variables that are of the order of the number of states.

@@

It is natural to expect that approximations lead to errors and it is important to quantify the errors. For a given ADP method, theoretical performance analysis involves  bounding the error terms $||J^*-\tilde{J}||$  and $\norm{J^*-J_{\tu}}$ which denote the error in approximating the value function, and performance loss due to following policy $\tu$ respectively (where $\norm{\cdot}$ is an appropriate norm). Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$). The focus of this paper is to present the error analysis for generalized reduced linear programming (GRLP), a new ADP formulation which we introduce in \Cref{sec:grlp}.
\end{comment}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Background} %: Markov Decision Processes (MDPs)}
%The framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems in stochastic environments. In this section, we present a brief overview of the MDP framework, introducing the notions of policy, value function and optimality (please refer to \cite{BertB} for a detailed presentation on MDP).
The purpose of this section is to introduce the necessary background before we can present the problem studied and the main results.

We shall consider finite state-action space, discounted total expected reward MDPs.
We note in passing that the assumption that number of states is finite is mainly made for convenience and at the expense of a more technical presentation could be lifted. We will comment later on the assumption concerning the number of actions.
Let the set of states, or state space be $\S = \{1,2,\dots,S\}$ and let the set of actions be $\A = \{1,2,\dots,A\}$. \todoc{$\S$ is for state space, $S$ for number of states, $\A$, $A$, similarly. Thus, $S=n$, $A=d$.}
For simplicity, we assume that all actions are admissible in all states. 
Given a choice of an action $a\in \A$ in a state $s\in \S$, the controller incurs a reward (or gain) of $g_a(s)\in [0,1]$ 
and the state moves to a next state $s'\in \S$ with probability $p_{a}(s,s')$. 
A \emph{policy} $u$ is a mapping from states to actions.\footnote{For the scope of this paper, it suffices to restrict our attention to such policies as opposed to considering history dependent policies. See Chapter 3, and specifically Corollary 3.3 of \cite{Kall17}.}
When a policy is followed, the state sequence evolves as a Markov chain with transition probabilities given by $P_u$ matrix whose $(s,s')$th entry is $P_{u(s)}(s,s')$. Along the way the rewards generated from $g_u$ defined by $g_u(s) \defeq g_{u(s)}(s)$.
The \emph{value} of following a policy from a starting state $s$ is denoted by $J_u(s)$ and is defined as 
the expected total reward discounted reward. Thus,
%The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$. We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.

%\textbf{Policy:} A stationary deterministic policy(SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state. Under an SDP, an MDP is a Markov chain whose probability transition matrix is denoted by $P_u$.

%\textbf{Value Function:} Given an SDP $u$, the expected total discounted reward corresponding to starting at a state $s\in S$ at $t=0$, while choosing actions as dictated by $u$ for the states encountered in the future (i.e., $t>0$), is
\begin{align}
%J_u(s)\stackrel{\Delta}{=}\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
J_u(s)\defeq \sum_{t=0}^\infty \alpha^t (P_u^t g_u)(s)\,,\nn
%\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
\end{align}
where  $\alpha \in (0,1)$ is the so-called discount factor. % and $s_{t+1} \sim p_{a_t}(s_t,\cdot)$, $t\ge 0$.
We call $J_u$ the \emph{value function} of policy $u$. The value function of a policy satisfies the fixed-point equation $J_u = T_u J_u$ where the affine-linear operator $T_u$ is defined by $T_u J = g_u + \alpha P_u J$.
An \emph{optimal policy}, is one that maximizes the value simultaneously for all initial states.
The \emph{optimal value function} $J^*$ is defined by $J^*(s) = \max_u J_u(s)$ and is known to be the solution of the fixed-point equation $J^* = T J^*$ where the operator $T$ is defined by $(TJ)(s) = \max_u (T_u J)(s)$, $s\in \S$, i.e., the maximization is component-wise. Optimal policies exist and in fact any policy $u$ such that the equation $T_u J^* = T J^*$ holds is optimal (e.g., Corollary 3.3 of \cite{Kall17}). A policy $u$ is said to be \emph{greedy} with respect to (w.r.t.) $J$ if $T_u J = T J^*$. Thus, any policy that is greedy w.r.t. $J^*$ is optimal.

\if0
The value functions $J_u$ is an elements of $\R^S$. In what follows it will be useful for us to treat it as an $n$-dimensional vector, i.e., an element of $\R^n$, effectively identifying $\R^S$ with $\R^n$ in the natural way. Similarly we identify $\R^{nd}$ with $\R^{S\times A}$, where $d=|A|$.

\textbf{Optimality and the Bellman Equation:} The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state. That is, $J_{u^*}(s) = J^*(s) \eqdef \us{\max}{u\in U} J_u(s)$
where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.
\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}
Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE) which states that for all $ s \in S$,
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),~\text{and}\\
\label{bellpol}u^*(s)&\in \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),\,.
\end{align}
\end{subequations}
where ties in \eqref{bellpol} are resolved arbitrarily.
For the subsequent sections, the following definitions will be useful later:
\begin{definition}\label{notations}
\begin{comment}
Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$,
define
\end{comment}
\begin{enumerate}[(i)]
\item\label{bellopval} The Bellman operator $T\colon \R^n \ra \R^n$ is given by $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
$
\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values is given by $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
\item\label{emat} The $nd\times n$ matrix $E$ is given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
\item\label{greedy} A policy $u_J$ is said to be greedy with respect to (w.r.t.) $J\in \R^n$ if for any $s\in S$,
%some function $\tj:S \to \R$
\begin{align*} u_J(s)\in\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S} p_a(s,s')J(s')\big).\end{align*}
\item\label{norms} The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ with respect to a probability distribution $c$ is given by $
\norm{J}_{1,c}=\sum_{s \in S} c(s)|J(s)|$.
\item The (un)weighted $L_\infty$-norms $\norm{\cdot}_{1,\infty}$
and $\norm{\cdot}_{\infty,\rho}$, $\norm{J}_{\infty}=\max_{s\in S}|J(s)|$ and $\norm{J}_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
\item For $J_1, J_2\in \R^n$ we write $J_1\leq J_2$ when $J_1(s)\leq J_2(s),~\forall s\in S$.
\item We define $\one\in \R^n$ to be the vector whose coordinates are all equal to $1$.
\end{enumerate}
\end{definition}
We would like to point out that from \Cref{notations}, it follows that for any $J\in \R^n$ the condition $J\geq TJ$ can be rephrased as $EJ\geq HJ$.
\begin{comment}
\subsection{Dynamic Programming: Objective and Methods}
Once a given sequential decision making is cast in the MDP framework, it remains for us to still compute the optimal policy $u^*$. The idea behind Dynamic Programming (DP) methods is to use the BE \eqref{bellval} to first compute $J^*$, and then a near-optimal action $u^*$ can be obtained via \eqref{bellpol}
for each state relatively cheaply even for large state-spaces (e.g., having the ability to sample from the next-state distribution at
a given state-action pair). Thus computing $J^*$ is at the heart DP methods \cite{BertB} such as value-, or policy-iteration and linear programming (LP) \eqref{mdplp} which can be used in practice when the MDP has a tractable number of states. However, when the MDP has a large number of states, using DP methods to obtain $J^*$ is tedious, since they involve computations in variables that are of the order of the number of states.

@@

It is natural to expect that approximations lead to errors and it is important to quantify the errors. For a given ADP method, theoretical performance analysis involves  bounding the error terms $||J^*-\tilde{J}||$  and $\norm{J^*-J_{\tu}}$ which denote the error in approximating the value function, and performance loss due to following policy $\tu$ respectively (where $\norm{\cdot}$ is an appropriate norm). Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$). The focus of this paper is to present the error analysis for generalized reduced linear programming (GRLP), a new ADP formulation which we introduce in \Cref{sec:grlp}.
\end{comment}
\fi
